\subsection{Images}

In order to handle simple error propagation tasks HDRL provides an
image class \verb+hdrl_image+ which is similar to \verb+cpl_image+.
It carries both the data values and their associated errors and also
contains a bad pixel mask in form of a binary cpl\_mask.  When crating
a new \verb+hdrl_image+ from two existing cpl images (\textit{image}
and \textit{error}) by using the function
\verb+hdrl_image_create(image, error)+, the bad pixel mask of the
passed error-image (\textit{error}) is completely ignored. The bad
pixel mask associated with the passed image (\textit{image}) becomes
the only relevant bad pixel mask. Moreover, \verb+hdrl_image_create+
creates the relevant \verb+hdrl_image+ by copying the cpl images.
Basic arithmetic operations, like addition, subtraction,
multiplication, division, and collapse operations (mean, median, sum,
...) involving \verb+hdrl_image+ propagate the errors according to
linear error propagation theory.  Correlations between data is
currently not accounted for. 

Some operations, e.g division can add new bad pixels when the value
can not be calculated, e.g. $x \div 0$.  Moreover, if a value can be
calculated but the corresponding propagated error can not (e.g. the
propagated error would be $0 \div 0$), the tuple value-error is still
considered valid, i.e. not marked as a bad pixel.
 
The API of \verb+hdrl_image+ is similar to \verb+cpl_image+, please refer to
the API reference for details.

\subsubsection{Example usage}

\begin{lstlisting}
hdrl_image * my_function(cpl_image * input_image,
                         cpl_image * input_errors
                         const hdrl_image * bias1,
                         const hdrl_image * bias2,
                         double scale)
{
    /* create new hdrl_image from input images */
    hdrl_image * data = hdrl_image_create(input_image, input_errors);

    /* take mean with error propagation
       equivalent to hdrl_imagelist_collapse */
    hdrl_image * master_bias = hdrl_image_duplicate(bias1);
    hdrl_image_add_image(master_bias, bias2);
    hdrl_image_div_scalar(master_bias, 2., 0.);

    /* subtract bias with error propagation */
    hdrl_image_sub_image(data, master_bias);

    /* reject a pixel */
    hdrl_image_reject(data, 1, 1);
    hdrl_image_delete(master_bias);

    return data;
}
\end{lstlisting}
